Self Regulation Ontology Retest Data Report

### 2017-11-16 code/SRO_Report.Rmd
cleaning up report

```{r warning=FALSE, message=FALSE}
boot_df %>%
  ggplot(aes(icc, fill = task))+
  geom_histogram(alpha=0.5, position='identity')+
  theme_bw()+
  theme(legend.title = element_blank())+
  xlab("ICC")
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')

@@

ggsave('Bootstrap_Var_Plot.jpg', plot = p6, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 36, height = 72, units = "in", limitsize = FALSE, dpi=50)

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Var_Plot.jpg')
```

@@

```{r warning=FALSE, message=FALSE}
rel_df %>%
  select(dv, task, spearman, pearson, icc) %>%
  gather(key, value, -dv, -task) %>%
  ggplot(aes(value, fill=task))+
  geom_histogram(alpha = 0.5, position = 'identity')+
  facet_wrap(~key)+
  theme_bw()+
  theme(legend.position = 'bottom',
        legend.title = element_blank())+
  xlab("")

>>>>

```{r warning=FALSE, message=FALSE}
boot_df %>%
  ggplot(aes(icc, fill = task))+
  geom_histogram(alpha=0.5, position='identity')+
  theme_bw()+
  theme(legend.title = element_blank())+
  xlab("ICC")

ggsave('Hist_Boot_Rel.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 6, height = 4, units = "in", limitsize = FALSE, dpi = 72)
```

@@

```{r warning=FALSE, message=FALSE}
# Df wrangling for plotting
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')

@@

ggsave('Bootstrap_Raw_Var_Plot.jpg', plot = p6, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 36, height = 72, units = "in", limitsize = FALSE, dpi=50)

@@

```{r echo=FALSE, out.width='100%'}
knitr::include_graphics('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/Bootstrap_Raw_Var_Plot.jpg')
```

@@

```{r warning=FALSE, message=FALSE}
boot_df %>%
  select(dv, task, spearman, pearson, icc) %>%
  gather(key, value, -dv, -task) %>%
  ggplot(aes(value, fill=task))+
  geom_histogram(alpha = 0.5, position = 'identity')+
  facet_wrap(~key)+
  theme_bw()+
  theme(legend.position = 'bottom',
        legend.title = element_blank())+
  xlab("")

# rel_df %>%
#   select(dv, task, spearman, pearson, icc) %>%
#   gather(key, value, -dv, -task) %>%
#   ggplot(aes(value, fill=task))+
#   geom_histogram(alpha = 0.5, position = 'identity')+
#   facet_wrap(~key)+
#   theme_bw()+
#   theme(legend.position = 'bottom',
#         legend.title = element_blank())+
#   xlab("")
